---
title: "R Exercises Session 8"
author: "Kristen Kolb"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Check your work by knitting the document.

1. Create a level 2 header below in Markdown with the name "Answer 1".

2. Add an unordered Markdown list of your favorite food dishes and
add their ingredients as sub-items in the list. You should enter at least two
dishes with two ingredients each.


3. Insert an R code chunk below. Show the `summary` of the `Orange` dataset.
Run a linear regression using the `lm` function to predict `circumference` from
`age` and assign the result. Show the `summary` of the fit object that you
assigned.


4. Add an RMarkdown weblink (in link format) below to your favorite R reference
website.


5. Replace the author field in the `yaml` header with your name and then
successfully `knit` the RMarkdown document into a Word document.


6. Follow the [Pull Request instructions on GitHub](https://help.github.com/en/github/collaborating-with-issues-and-pull-requests/creating-a-pull-request-from-a-fork)
to submit your assignment via GitHub as a Pull Request to the [Assignment8][1]
repository.

[1]: https://github.com/CUNYSPHCode/Assignment8

## Answer 1

### Favorite food ingredients

- Pizza
  - Dough
  - Sauce
  - Cheese
  
- Ice Cream
  - Milk
  - Cream
  - Sugar
  
- Sandwich
  - Bread
  - Meat
  - Cheese
  - Mayo
  
## Answer 2
  
```{r}
data("Orange")
summary(Orange)
result <-lm(circumference~age, data = Orange)
summary(result)
```

## Answer 3

#### R reference website: 

[R Tutorial](https://www.tutorialspoint.com/r/index.htm)

